---
title: "Download videos/audios from YouTube by youtubeDownloader"
author: "Weiyang Tao"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_document:
    highlight: pygments
    toc: true
    number_sections: true
    fig_width: 5
vignette: >
  %\VignetteIndexEntry{Download videos/audios from YouTube}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r, warning=FALSE}
library(devtools)
library(youtubeDownloader)
```

# Installing required softwares
According to the output of \code{installDownloader} function to install required softwares: youtube_dl and ffmpeg.
The youtube_dl is a python package, which is used to trace the true video URL from YouTube.
The ffmpeg software is to convert video/audio formats.
```{r}
installDownloader()
```


# Downloading a list of videos
```{r, eval=FALSE}
# Sequence.Models
url0 = "https://www.youtube.com/watch?v=DejHQYAGb7Q&list=PLkDaE6sCZn6F6wUI9tvS_Gw1vaFAx6rd6"
# the folder to save downloaded files
folder = "/data/surfDrive/TutorialVideos/" 

# #### download audio
newFolder = videoListDownload(urlSeed = url0, path = folder, 
                              saveFileList = TRUE, 
                              sleepTime = 5, maxDownload = 200, 
                              bothVideoAudio = TRUE)
```

# Downloading a list of audios
```{r, eval=FALSE}
url0 = "https://www.youtube.com/watch?v=DejHQYAGb7Q&list=PLkDaE6sCZn6F6wUI9tvS_Gw1vaFAx6rd6"
# #### Only download audio
newFolder = videoListDownload(urlSeed = url0, path = folder, 
                              saveFileList = TRUE, 
                              sleepTime = 5, maxDownload = 200, 
                              priority = c("audio only"), 
                              bothVideoAudio = FALSE)
```


# Downloading one single audio
```{r, eval=FALSE}
url0 = "https://www.youtube.com/watch?v=J9NQFACZYEU&list=PLMC9KNkIncKtPzgY-5rmhvj7fax8fdxoj&index=PLMC9KNkIncKtPzgY-5rmhvj7fax8fdxoj"

youTubeDownload(url0, path = paste0(folder, "music"),
                saveFile = "videoFromYoutube", 
                priority = "audio only", 
                bothVideoAudio = FALSE)
# .webm to .mp3 format
tmp = audio2mp3(fileFormat = "webm", path = newFolder, 
                removeSource = TRUE)
```


# Downloading one single video
```{r, eval=FALSE}
url0 = "https://www.youtube.com/watch?v=pJON0-e_I3o&t=889s"
#### download video
youTubeDownload(url0, path = "./OneVideo", 
                saveFile = "videoFile",
                priority = c("best", "mp4"))
```


# Downloading videos by table
```{r, eval=FALSE}
file = "fileNameOrders.csv"
folderName = paste0(folder, "fileByTable")
#### download video by fileNameOrders.csv table
newFolder = videoListDownloadByTable(fileList = file, 
                                     folderName = folderName, 
                                     bothVideoAudio = TRUE, 
                                     priority = c("best"), 
                                     sleepTime = 10, 
                                     id = c(1, 2, 5, 9))
```


# Converting video format 
```{r, eval=FALSE}
# .webm to .mp4 format
vidio2mp4(fileFormat = "webm", path = newFolder, 
          removeSource = FALSE)
```


# Converting audio format 
```{r, eval=FALSE}
# .webm to .mp3 format
audio2mp3(fileFormat = "webm", path = newFolder, 
          removeSource = FALSE)
```

# SessionInfo
```{r}
session_info()
```

